Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-13 ms.qmd
tensor update

  # Model lat and long....

   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + long.x*lat.y + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)

@@

# Lets now make some predictions 
#conditional_effects(model5_bayes)

pred <- conditional_effects(model5_bayes)
pp_check(model5_bayes)
```

>>>>

  # Model lat and long. Need to exclude missing acclimdation data. That will make it easier to create predcitions and explore the model fit.

   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + t2(long.x, lat.y) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])

@@

# Lets explore the model and how it's predciting the real data
  data_w_pred <- cbind(lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),], predict(model5_bayes))
  head(data_w_pred)

# Fitted vs actual data
  ggplot(data = data_w_pred, aes(x = Estimate, y = effect_size)) + geom_point() + geom_smooth(method = "lm") + labs(x = "Predicted Effect Size", y = "Observed Effect Size") + theme_classic() + 
  geom_abline(intercept = 0, slope = 1)

# Fitted by Lat/long
  ggplot(data = data_w_pred, aes(y = Estimate, x = lat.y)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()

  ggplot(data = data_w_pred, aes(y = Estimate, x = long.x)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()

# Observed by Lat/long
  ggplot(data = data_w_pred, aes(y = effect_size, x = lat.y)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()

  ggplot(data = data_w_pred, aes(y = effect_size, x = long.x)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
